Analysis for Project

### 2021-11-17 analysis/analysis.Rmd
Fix a few things from previous commit
Fixed a few typos and supressed warnings in  code chunks that call marg

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, as.factor(year)+current_grade+as.factor(state)+metro)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

@@

```{r cond-means-model4}
coef_table_mod4 <- calculate_cond_means(model4)

@@

```{r cond-means-model-compare, fig.height=12}
#calculate remaining marginal means
coef_table_mod1 <- calculate_cond_means(model1)
coef_table_mod2 <- calculate_cond_means(model2)

>>>>

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, .~.+as.factor(year)+current_grade+as.factor(state)+metro)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

@@

```{r cond-means-model4, warning=FALSE}
coef_table_mod4 <- calculate_cond_means(model4)

@@

```{r cond-means-model-compare, fig.height=12, warning=FALSE}
#calculate remaining marginal means
coef_table_mod1 <- calculate_cond_means(model1)
coef_table_mod2 <- calculate_cond_means(model2)
